---
title: "Homework_04"
author: "Ely P. Remes"
date: "2024-02-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Suppose x = 1.1, a = 2.2, and b = 3.3. Assign each expression to the value of the variable z and print the value stored in z.

x^a^b

(x^a)^b

3x^3 + 2x^2 +1

```{r, echo = TRUE}


x <- 1.1
a <- 2.2
b <- 3.3


z <- (x^(a^b)) 

print(z)

z <- ((x^a)^b)

print(z)

z <- (3*x^3+2*x^2+1)

print (z)
```


Using the rep and seq functions, create the following vectors:

(1,2,3,4,5,6,7,8,7,6,5,4,3,2,1)
(1,2,2,3,3,3,4,4,4,4,5,5,5,5,5)
(5,4,4,3,3,3,2,2,2,2,1,1,1,1,1)

```{r echo = TRUE}

y<- seq(from = 1, to = 8, by = 1)
a <-seq(from = 7, to = 1, by = -1)
z <- c(y,a)

print(z)


y <- seq(1:5)

d <- rep(y , time=y)

print(d)

d <- rep(rev(y) , time=y)

print (d)
```


Create a vector of two random uniform numbers. In a spatial map, these can be interpreted as x and y coordinates that give the location of an individual (such as a marked forest tree in a plot that has been mapped). Using one of R’s inverse trigonometry functions (asin(), acos(), or atan()), convert these numbers into polar coordinates 
```{r, echo=TRUE}
x <- 5 #Set x coordinate
y <- 105 #Set y coordinate
Cartesian <- c(x,y)

print(Cartesian)
r <- sqrt((x^2) +(y^2)) # Find r
Theta <- acos(x/r)

Polar <- c(r,Theta)


print(Polar)
```

Create a vector queue <- c("sheep", "fox", "owl", "ant") where queue represents the animals that are lined up to enter Noah’s Ark, with the sheep at the front of the line. Using R expressions, update queue as:

the serpent arrives and gets in line;
the sheep enters the ark;
the donkey arrives and talks his way to the front of the line;
the serpent gets impatient and leaves;
the owl gets bored and leaves;
the aphid arrives and the ant invites him to cut in line.
Finally, determine the position of the aphid in the line.

```{r, echo=TRUE}

queue <- c("sheep", "fox", "owl", "ant")
print(queue)
queue <- c(queue, "serpent")
print(queue)
queue <- c(queue[2:5])
print(queue)
queue <- c("donkey", queue [1:4])
print(queue)
queue <- c(queue [1:4])
print(queue)
queue <- c(queue [1:2], queue [4])
queue <- c(queue[1:2], "aphid", queue [3])
print(queue)
print (which( "aphid" == queue))
```


Use R to create a vector of all of the integers from 1 to 100 that are not divisible by 2, 3, or 7.

```{r , echo=TRUE}
a <- 1:100

b <- which((a%%2!=0) & (a%%3!=0) & (a%%7!=0))
print(b)
```