---
title: "Homework_10"
author: "Ely P. Remes"
date: "2024-04-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 1


Using a for loop, write a function to calculate the number of zeroes in a numeric vector. Before entering the loop, set up a counter variable counter <- 0. Inside the loop, add 1 to counter each time you have a zero in the vector. Finally, use return(counter) for the output.

```{r}
source("Homework_09Functions.R")
x<- rep(1:10, times=25)

rows<-5
columns<-4

zero_counter<-function(vec){

  counter<-0
  for (i in vec){
    if (i == 0){
      counter<- counter+1
    }
  }
  
  return(counter)
}
print(zero_counter(vec=x))
```

### Question 2


Use subsetting instead of a loop to rewrite the function as a single line of code.
```{r}
SubsetOfZero<-function(vec){
  return(sum(vec == 0))
}
print(SubsetOfZero(vec=x))  
```

### Quetion 3


Write a function that takes as input two integers representing the number of rows and columns in a matrix. The output is a matrix of these dimensions in which each element is the product of the row number x the column number.
```{r}
EasyMatrix<-function(rows=x,columns=y){
  
  m<-matrix(nrow=rows,ncol=columns)
  for(i in 1:nrow(m)) {
    for(j in 1:ncol(m)) {
     m[i,j]<- i*j
    }
  }
  return(m)
}
EasyMatrix(rows=7,columns=3)
```

### Question 4A


Now let’s practice calling custom functions within a for loops. Use the code from previous lectures on loops and functions to complete the following steps:

Simulate a dataset with 3 groups of data, each group drawn from a distribution with a different mean. The final data frame should have 1 column for group and 1 column for the response variable

```{r}


nName= c("Potatoes","Carrots","Radishes")
nSize= c(rep(20, times=3))
nMean= c(17,25, 19)
nSD= c(runif(3))

VeggieWeight<-FakeDataGeneration()

print(head(VeggieWeight))

```

### Question 4B


Write a custom function that 1) reshuffles the response variable, and 2) calculates the mean of each group in the reshuffled data. Store the means in a vector of length 3.
```{r}
Randomizer<-function(x){
  
  
CleanWeight<-mutate(x, Treatment,Value=round(Value, digits=1))
NewWeight<-sample(CleanWeight$Value)
  
  
  
MixedWeight<-mutate(CleanWeight, Treatment, NewWeight)
MixedWeight<-select(MixedWeight, Treatment, NewWeight)

Answer<-group_by(MixedWeight, Treatment) %>% summarize(m = mean(NewWeight))
return(unlist(Answer[,2]))
}



print(head(Randomizer(x=VeggieWeight)))
```

### Question 4C


Use a for loop to repeat the function in b 100 times. Store the results in a data frame that has 1 column indicating the replicate number and 1 column for each new group mean, for a total of 4 columns.
```{r}
FrameWork<- data.frame(matrix(nrow=100,ncol=3))

for (i in 1:nrow(FrameWork)) {
  FrameWork[i,]<-Randomizer(x=VeggieWeight)
}

FrameWork<-mutate(FrameWork, ID=(1:100))
FrameWork<-select(FrameWork, ID,Potatoes=X1,Carrots=X2,Radishes=X3)

print(head(FrameWork))
```

### Question 4D


Use qplot() to create a histogram of the means for each reshuffled group. Or, if you want a challenge, use ggplot() to overlay all 3 histograms in the same figure. How do the distributions of reshuffled means compare to the original means?

```{r, echo=FALSE}

print(hist(x=FrameWork$Carrots, col="darkorange",length.out=8,xlab="Carrot Mean Distribution" ))
print(hist(x=FrameWork$Potatoes,
     col="tan3",length.out=8,
     xlab="Potato Mean Distribution"))
print(hist(x=FrameWork$Radishes,
     col="purple", length.out=8,
    xlab="Radish Mean Distribution" ))

```